---
title: '3.6'
output: html_document
date: "2023-06-25"
---

## 3.6 Linear Regression

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## 3.6.2: Simple Linear Regression

In this lab we use the Boston data set in MASS library, and try to predict `medv` using other variables

```{r}
library(MASS)
library(ISLR)
```

```{r}
Boston
```

We can run the regression by using `lm` function, and show the summary of the regression results:

```{r}
lmod=lm(medv~lstat, data=Boston)
lmod
```

And we can use `names` or `coef` to see details, and `confint` to see the confidence interval.

```{r}
names(lmod)
coef(lmod)
confint(lmod)
```

We can also use `predict` to see the prediction interval

```{r}
predict(lmod, data.frame(lstat=(c(5,10,15))), interval = "confidence")
predict(lmod, data.frame(lstat=(c(5,10,15))), interval = "prediction")
lstat
```

```{r}
plot(lstat, medv)
abline(lmod)
abline(lmod, lwd=3)
```

We can also use the `par` function to let pictures be splitted, and use `rstudent` or `residuals` to see detailed plots.

```{r}
par(mfrow=c(2,2))
plot(lmod)
plot(predict(lmod), residuals(lmod))
```

## 3.6.3 Multiple Regression

We basically need to use plus sign to perform multiple regression in R

```{r}
lmod2 = lm(medv~lstat+age, Boston)
lmod2
```

Or use `.` to regress on all variables

```{r}
lmod3 = lm(medv~., Boston)
lmod3
```

We can use `?summar$lmod` to see details. `summary(lomd)$sigma` gives RSE, and r.sq gives $R^2$

## 3.6.4 Interaction Terms

For interactions terms, we do
